Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-08-22 docs/paper/paper.Rmd
revert back to 19th of July data

  We extracted forecasts and data on notified weekly COVID-19 cases from the ECDC forecasting hub from 15th of January 2022 to the 15th of August 2022 for the ensemble model (referenced as `EuroCOVIDhub-ensemble` by the hub team) and the surrogate model (submitted as `epiforecasts-weeklygrowth`).
  We included all locations covered by the ECDC forecasting hub which were 32 European countries, including all countries of the European Union and European Free Trade Area, and the United Kingdom.
  Data on notified weekly cases was originally sourced from the Johns Hopkins University curated data repository (JHU, [@REF]).
  We used the latest available observed data. As observations are subject to revisions this means that the data used to produce forecasts for a given date may not reflect the data used for evaluation.
  The follows the common practice of the forecasting hub projects in treating the latest available data as the forecast target regardless of the number of data revisions.
  Incidence was aggregated over the Morbidity and Mortality Weekly Report (MMWR) epidemiological week definition of Sunday through Saturday.

@@

We extracted forecasts starting from the 15th of January until the 1st of August 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as `epiforecasts-EpiNow2` by the hub), and our surrogate model. Of the remaining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r nrow(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targeted at specific conditions.

>>>>

  We extracted forecasts and data on notified weekly COVID-19 cases from the ECDC forecasting hub from 15th of January 2022 to the 19th of July 2022 for the ensemble model (referenced as `EuroCOVIDhub-ensemble` by the hub team) and the surrogate model (submitted as `epiforecasts-weeklygrowth`).
  We included all locations covered by the ECDC forecasting hub which were 32 European countries, including all countries of the European Union and European Free Trade Area, and the United Kingdom.
  Data on notified weekly cases was originally sourced from the Johns Hopkins University curated data repository (JHU, [@REF]).
  We used the latest available observed data. As observations are subject to revisions this means that the data used to produce forecasts for a given date may not reflect the data used for evaluation.
  The follows the common practice of the forecasting hub projects in treating the latest available data as the forecast target regardless of the number of data revisions.
  Incidence was aggregated over the Morbidity and Mortality Weekly Report (MMWR) epidemiological week definition of Sunday through Saturday.

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as `epiforecasts-EpiNow2` by the hub), and our surrogate model. Of the remaining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r nrow(partial_models)` models submitted for between 3 and 30 locations and all these models varied the number of locations they submitted forecasts for over time, potentially indicating manual curation or models targeted at specific conditions.
